Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2022-03-01 papers/02 journal v2/journal_v14.tex
g

\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
\end{itemize}
From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage. From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
}
%
\begin{figure}[t]
\centering
\includegraphics[width=.3\textwidth]{figures/37bus_sys_f6}
\smallskip
\caption{\edit{Information flow in Algorithm 1.}}
\label{fig:IFC}
\end{figure}%
%
\begin{figure}[t]
\marginnote{\note{R1-6}}
\edit{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 1}. Coordinated P2P Market Clearing
\smallskip
\hrule 
\smallskip
\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$. DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\! 0$, $\mu_y^{\text{pb}}(0)\! = \!0$, $\forall y \!\in\! \mc B$.

\smallskip
 \text{Iterate until convergence $(k = 0,1,\ldots)$}
\begin{align*}
& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
\quad &\left|
\begin{array}{l}
\text{Local update via \textsc{Algorithm 2}:}\\
\left\lfloor
\begin{array}{l}
\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
\end{array}
\right.\\[1em]
 \text{Communication}\\
 \left\lfloor
\begin{array}{l}
\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
 \left\lfloor
\begin{array}{l}
p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
\end{array}
\right.
\end{array}
\right.
\end{array}
\right.\\[.5em]
%%%
% DNO
%%%
& \text{DNO}\\
\quad &\left|
\begin{array}{l}
\text{Central update via \textsc{Algorithm 3}:}\\
\left\lfloor
\begin{array}{l}
\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
\end{array}
\right.\\[1em]
\text{Communication (Gather \& Broadcast)}\\
 \left\lfloor
\begin{array}{l}
\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
 \left\lfloor
\begin{array}{l}
\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}} \text{ on bus } y%
\end{array}%
\right.%
\end{array}%
\right.\\[1em]
\end{array}
\right.%
\end{align*}
\smallskip
\hrule
\end{minipage}
}
\end{figure}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\marginnote{\note{R1-6}}
\edit{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 2}. Prosumer $i$'s local update
\smallskip
\hrule 
\smallskip
\text{Step sizes}: For each $i \in \mc N$, set $\alpha_{i} <1/(3+N\max_{h\in \mc H} d_h^{\mathrm{mg}})$, $\beta_{(i,j)}^{\text{tr}}=\beta_{(j,i)}^{\text{tr}} < 1/2$, for all $j \in \mc N_i$.\\
\medskip
\noindent 
(i) \text{Dual update (trading reciprocity):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
\text{For all } j \in \mc N_i \text{ (in parallel):}\\
\left\lfloor
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{tr}}_{(i,j)}(k)  =  p^{\textrm{tr}}_{(i,j)} (k) + p^{\textrm{tr}}_{(j,i)} (k)\\
\mu^{\text{tr}}_{(i,j)}(k) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
	2  \zeta^{\text{tr}}_{(i,j)}(k) - \zeta^{\text{tr}}_{(i,j)}(k\!-\!1)
	\right)
\end{array}
\right.
\end{array}
\right.
$

\medskip
\noindent
(ii) \text{Primal update (generation, storage, load, and trading):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
\psi_i(k) = u_i(k)-
	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
	\hspace*{5em}
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\
%
\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.2em]	
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	 J_{i} \big( \xi, u_{-i}(k) \big) 
	+ \frac{1}{2 \alpha_i}
	\left\| \xi -  \psi_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t.} & \xi \in \mc U_i
\end{array} 
	\right.
\end{array}	
\right.		$

@@

\medskip
\noindent 
(i) \text{Primal update (network physical variables):}\\[.2em]
\hspace*{.15em}
$\left|
\begin{array}{l}
\psi(k) = \col \left( 
	\left\{
	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B} \right)\\[.7em]
%
u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
\end{array}
\right.
$

\medskip
\noindent
\noindent 
(ii) \text{Dual update (operational feasibility):}\\[.2em]
\hspace*{.15em}
$
\left| 
\begin{array}{l}
%
\eta(k\!+\!1) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]\\
	%
	\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
	 \right)\\
%
\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
	%
	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
	%
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
\left\lfloor
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
%
\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
\end{array}
\right.
\end{array}
\right.
$

>>>>

\item a (dual) variable $\mu_{y}^{\text{pb}}$ for each bus $y \in \mc B$, associated with the power balance constraint on bus $y$ \eqref{eq:p_bal_p}.
\end{itemize}
From an economic perspective, these variables can be interpreted as extra marginal losses imposed to the prosumers for the grid usage. From a control-theoretic perspective, they can be interpreted as states of discrete-time integrators driven by the violation of the network operational constraints \eqref{eq:Cconstr_def}.
}
%
\begin{figure}[t!]
\centering
\includegraphics[width=.3\textwidth]{figures/37bus_sys_f7}
\smallskip
\caption{\edit{Information flow in Algorithm 1.}}
\label{fig:IFC}
\end{figure}%
%
\begin{figure}[t]
\marginnote{\note{R1-6}}
\edit{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 1}. Coordinated P2P Market Clearing
\smallskip
\hrule 
\smallskip
\text{Initialization}: For all prosumers $i \in \mc N$: set $\mu^{\text{tr}}_{(i,j)}(-1) = 0$, $\forall j \in \mc N_i$. DNO: set $\lambda^{\text{mg}}(0)\!=\!0$, $\mu^{\text{tg}}(0) \!=\! 0$, $\mu_y^{\text{pb}}(0)\! = \!0$, $\forall y \!\in\! \mc B$.

\smallskip
 \text{Iterate until convergence $(k = 0,1,\ldots)$}
\begin{align*}
& \text{For all prosumers $i \in \mc I$ (in parallel):}\\
\quad &\left\lfloor
\begin{array}{l}
\text{Local update via \textsc{Algorithm 2}:}\\
\left\lfloor
\begin{array}{l}
\text{Set $\{\mu_{(i,j)}(k)\}_{j \in \mc N_i}$ as in \textsc{Alg. 2} (i)}\\
\text{Set $u_i(k\!+\!1)$ as in \textsc{Alg. 2} (ii)}
\end{array}
\right.\\[1em]
 \text{Communication}\\
 \left\lfloor
\begin{array}{l}
\eta_i(k\!+\!1), \; p_i^{\text{mg}}(k\!+\!1) \rightarrow \text{ DNO}\\[.5em]
\text{For all trading partners } j \in \mc N_i \text{ (in parallel):}\\
 \left\lfloor
\begin{array}{l}
p_{(i,j)}^{\text{tr}}(k\!+\!1) \rightarrow \text{ prosumer } j
\end{array}
\right.
\end{array}
\right.
\vspace*{.1em}
\end{array}
\right.\\[.5em]
%%%
% DNO
%%%
& \text{DNO}\\
\quad &\left\lfloor
\begin{array}{l}
\text{Central update via \textsc{Algorithm 3}:}\\
\left\lfloor
\begin{array}{l}
\text{Set $u_{N+1}(k\!+\!1)$ as in \textsc{Alg. 3} (i)}\\
\text{Set $\lambda^{\text{mg}}$, $\mu^{\text{tg}}$, $\{ \mu_y^{\text{pb}}(k\!+\!1)\}_{y \in\mc B}$ as in \textsc{Alg. 3} (ii)}
\end{array}
\right.\\[1em]
\text{Communication (Gather \& Broadcast)}\\
 \left\lfloor
\begin{array}{l}
\sigma^{\mathrm{mg}},\, \lambda^{\text{mg}}, \mu^{\text{tg}}(k\!+\!1) \rightarrow \text{ all prosumers } i \in \mc N\\[.5em]
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
 \left\lfloor
\begin{array}{l}
\mu_y^{\text{pb}}(k+1) \rightarrow \text{ all prosumers } i \in \mc N_y^{\text{b}} \text{ on bus } y%
\end{array}%
\right.%
\end{array}%
\right.
\vspace*{.1em}
\end{array}
\right.%
\end{align*}
\smallskip
\hrule
\end{minipage}
}
\end{figure}%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\marginnote{\note{R1-6}}
\edit{
\begin{minipage}{\columnwidth}
\hrule
\smallskip
\textsc{Algorithm 2}. Prosumer $i$'s local update
\smallskip
\hrule 
\smallskip
\text{Step sizes}: For each $i \in \mc N$, set $\alpha_{i} <1/(3+N\max_{h\in \mc H} d_h^{\mathrm{mg}})$, $\beta_{(i,j)}^{\text{tr}}=\beta_{(j,i)}^{\text{tr}} < 1/2$, for all $j \in \mc N_i$.

\medskip
\noindent 
(i) \text{Dual update (trading reciprocity):}\\[.2em]
\hspace*{.15em}
$
\left\lfloor
\begin{array}{l}
\text{For all } j \in \mc N_i \text{ (in parallel):}\\
\left\lfloor
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{tr}}_{(i,j)}(k)  =  p^{\textrm{tr}}_{(i,j)} (k) + p^{\textrm{tr}}_{(j,i)} (k)\\
\mu^{\text{tr}}_{(i,j)}(k) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
	2  \zeta^{\text{tr}}_{(i,j)}(k) - \zeta^{\text{tr}}_{(i,j)}(k\!-\!1)
	\right)
\end{array}
\right.
\vspace*{.1em}
\end{array}
\right.
$

\medskip
\noindent
(ii) \text{Primal update (generation, storage, load, and trading):}\\[.2em]
\hspace*{.15em}
$
\left\lfloor
\begin{array}{l}
%\text{Receive } \sigma^{\mathrm{mg}}(k),\, \lambda^{\text{mg}}(k), \mu^{\text{tg}}(k), \mu_y^{\text{pb}}(k) \text{ from the DNO}\\
\psi_i(k) = u_i(k)-
	\alpha_i \cdot \col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}\\
	\hspace*{5em}
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)\\
%
\text{Set } u_i(k\!+\!1) \text{ as the unique solution to}\\[.2em]	
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	 J_{i} \big( \xi, u_{-i}(k) \big) 
	+ \frac{1}{2 \alpha_i}
	\left\| \xi -  \psi_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t.} & \xi \in \mc U_i
\end{array} 
	\right.
	\vspace*{.1em}
\end{array}	
\right.		$

@@

\medskip
\noindent 
(i) \text{Primal update (network physical variables):}\\[.2em]
\hspace*{.15em}
$\left\lfloor
\begin{array}{l}
\psi(k) = \col \left( 
	\left\{
	\0,\mu^{\text{tg}}(k) + \mu_y^{\text{pb}}(k), 
	\{ \mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B} \right)\\[.7em]
%
u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) + (\alpha_{N+1})^{-1} \psi(k) \right)
\vspace*{.1em}
\end{array}
\right.
$

\medskip
\noindent
\noindent 
(ii) \text{Dual update (operational feasibility):}\\[.2em]
\hspace*{.15em}
$
\left\lfloor
\begin{array}{l}
%
\eta(k\!+\!1) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]\\
	%
	\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta(k\!+\!1)
	 \right)\\
%
\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k\!+\!1)+b- \sigma^{\text{tg}}(k\!+\!1)\\
	%
	\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))\\[.5em]
	%
\text{For all busses } y \in \mc B \text{ (in parallel):}\\
\left\lfloor
\begin{array}{l}
%\text{Receive } p^{\textrm{tr}}_{(j,i)} (k) \text{ from prosumer } j\\
\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k\!+\!1)\\
\hspace*{9em} - p^{\text{tg}}_y(k\!+\!1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k\!+\!1)\\[.5em]
%
\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k\!+\!1)- \zeta^{\text{pb}}_y(k))
\end{array}
\right.
\vspace*{.2em}
\end{array}
\right.
$
